Unrestricted Termination and Non-Termination Arguments for Bit-Vector Programs\thanks{Supported by UK EPSRC EP/J012564/1 and ERC project 280053.}

### 2014-12-14 papers/termination/termination-esop/paper.tex
thanks and SV-COMP

\title{Unrestricted Termination and Non-Termination Arguments for Bit-Vector Programs}

@@

To evaluate our algorithm, we implemented a tool that generates a
termination specification from a C program and calls the second-order SAT solver in \cite{kalashnikov} to obtain a proof.
We ran the resulting termination prover,
named {\sc Juggernaut}, on 47
benchmarks taken from the literature and
SV-COMP'15~\cite{svcomp15}.
We omitted exactly those SVCOMP'15
benchmarks that made use of arrays or recursion. We do not have arrays in
our logic and we had not implemented recursion in our frontend (although the
latter can be syntactically rewritten to our input format).

>>>>

\title{Unrestricted Termination and Non-Termination Arguments for Bit-Vector
Programs\thanks{Supported by UK EPSRC EP/J012564/1 and ERC project 280053.}}

@@

To evaluate our algorithm, we implemented a tool that generates a
termination specification from a C program and calls the second-order SAT solver in \cite{kalashnikov} to obtain a proof.
We ran the resulting termination prover,
named {\sc Juggernaut}, on 47
benchmarks taken from the literature and
SV-COMP'15~\cite{svcomp15}.
We omitted exactly those SV-COMP'15
benchmarks that made use of arrays or recursion. We do not have arrays in
our logic and we had not implemented recursion in our frontend (although the
latter can be syntactically rewritten to our input format).
